\documentclass[10pt,a4paper]{report}
\parindent 0pt 
\parskip 2ex
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\author{Emmanuel Obonyo 14/u/13713/PS 214012922}
\title{The Church In Africa}
\begin{document}
•\maketitle The Major Cause of The Decline of The Church
 \\
 \\ I believe the major cause of the decline of the Church in Africa as a whole is because has been made too spiritualistic to solve any physical problems. The way the gospel is being preached puts it somewhere in the clouds; making it out of the reach of 'ordinary' human beings and therefore making the message useless to man. The church has focused on preaching on heaven and hell. The major message, even as you move through the streets of Uganda is: 'Get saved or suffer the consequences': The population is suffering from diseases, poverty, corruption and failed marriages; many of them are already living in a hell of sorts and therefore the idea of hell is not very frightening to them. They don't believe hell can be any worse than this. Many people in church are living on poverty, and bad marriages and sickness because of the doctrine they are receiving. The outer crowd looks at these Christians and decides that they don't want anything to do with them. 
\\
\\The church is not talking about unemployment or families. They're only focusing on taking people to heaven. Basically the idea is; Go through the tribulations here on earth and have a have a great time in heaven where there is no more crying and the streets are paved of gold. Basically they are preaching a God that wants you to cry now so that you can enjoy heaven; In other words, whatever heaven is like, you'll enjoy it since you cried your way through earth. 
\\
\\Another major problem is the redundancy and the spectators that the congregation has been turned to. The congregation gathers every Sunday to listen to a Pastor or Spiritual lead because the apparently the spiritual lead knows all. In some congregations, the opinion of the spiritual head is doctrine and can not be argued with because they know all. The congregation is not empowered at all to do anything. All the spiritual growth of the congregation, sometimes of more than one thousand people, is dropped on the spiritual head. This has led to a lot of exploitation that has left a lot of people hurt. Some of these church leaders have been got in different scandals and this has brought great distress and hurt to the congregation because they have trusted them and elevated them to almost god status and therefore they feel betrayed. They church will fall because all the  responsibility to grow and lead the church was on one person who has now betrayed everyone. 
\\
\\They is also a lot of annoying finger pointing. Everyone says that the other church is wrong. Spiritual heads that are supposed to bring about unity are condemning other churches and therefore causing distrust between the different congregations. Instead of looking beyond the belief system and loving them as a person, they say that the other people are of the devil. Even if they are, they are still people and need to be loved as people and love can cross boundaries that religion can't. There is too much division in the church that people look at and conclude that they don't want anything to do with it. 
\\
\\\maketitle The solution
\\ We need to create an involved congregation that is encouraged to read the word of God for themselves. That is allowed to think and challenge what they read and hear and should not be mere puppets for the spiritual leads to manipulate. The church needs to resolve issues here on earth and be relevant to the communities: solving issues from corruption to witch craft.  
\end{document}